Waveform and Passive Beamforming Design for Intelligent Reflecting Surface-Aided Wireless Information and Power Transfer

### 2020-08-14 main.tex
:art: Convergence proof

			\textbf{Proposition 1}. \textit{For any feasible initial point, the proposed SCA-based Algorithm \ref{al:irs} is guaranteed to converge to a stationary point of the IRS phase shift subproblem.}

			\textit{Proof:} The objective function \ref{ob:irs} is non-decreasing over iterations because the solution of problem \ref{op:irs} at iteration $i-1$ is still a feasible point at iteration $i$. Moreover, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \ref{co:irs_modulus}. Thus, Algorithm \ref{al:irs} is guaranteed to converge. To prove $\boldsymbol{\Phi}^{(i)}$ converge to the set of stationary points of IRS subproblem, we notice that the SCA-based Algorithm \ref{al:irs} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$, and the approximation \ref{eq:taylor_1} -- \ref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Adali2010,Li2013}. Therefore, Algorithm \ref{al:irs} converges to a stationary point.

			\textbf{Proposition 2}. \textit{For any feasible initial point, the GP-based Algorithm \ref{al:waveform} is guaranteed to converge to a stationary point of the waveform and splitting ratio subproblem.}

			\textit{Proof:} See \cite{Clerckx2016a,Clerckx2018b}.

			\textbf{Proposition 3}. \textit{Every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_I^{\star},\boldsymbol{w}_P^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem \ref{op:original}.}

			\textit{Proof:} The objective function \ref{ob:original} is non-decreasing over iterations of Algorithm \ref{al:alternating}, which is also upper-bounded due to the unit-modulus constraint \ref{co:original_modulus} and the average transmit power constraint \ref{co:original_power}. Thus, Algorithm \ref{al:alternating} is guaranteed to converge, namely the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_I^{(i)},\boldsymbol{w}_P^{(i)},\rho^{(i)}\}$ generated by optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$ alternatively has limit points. As demonstrated in \cite{Grippo2000,Hong2016,Li2013a}, the solution is a stationary point of problem \ref{op:original}.
		\end{subsubsection}
	\end{subsection}
\end{section}

>>>>

			\begin{proposition}\label{pr:irs}
				For any feasible initial point, the proposed SCA-based Algorithm \ref{al:irs} is guaranteed to converge to a stationary point of the IRS phase shift subproblem.
			\end{proposition}

			\begin{proof}\label{pf:irs}
				The objective function \ref{ob:irs} is non-decreasing over iterations because the solution of problem \ref{op:irs} at iteration $i-1$ is still a feasible point at iteration $i$. Moreover, the sequence $\{\tilde{z}(\boldsymbol{\Phi}^{(i)})\}_{i=1}^{\infty}$ is bounded above due to the unit-modulus constraint \ref{co:irs_modulus}. Thus, Algorithm \ref{al:irs} is guaranteed to converge. To prove $\boldsymbol{\Phi}^{(i)}$ converge to the set of stationary points of IRS subproblem, we notice that the SCA-based Algorithm \ref{al:irs} is indeed an inner approximation algorithm \cite{Marks1978}, since $\tilde{z}(\boldsymbol{\Phi}) \le z(\boldsymbol{\Phi})$, $\partial\tilde{z}(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}=\partial z(\boldsymbol{\Phi}^{(i)})/\partial\boldsymbol{\Phi}$, and the approximation \ref{eq:taylor_1} -- \ref{eq:taylor_3} are asymptotically tight as $i \to \infty$ \cite{Adali2010,Li2013}. Therefore, Algorithm \ref{al:irs} converges to a stationary point.
			\end{proof}

			\begin{proposition}\label{pr:waveform}
				For any feasible initial point, the GP-based Algorithm \ref{al:waveform} is guaranteed to converge to a stationary point of the waveform and splitting ratio subproblem.
			\end{proposition}

			\begin{proof}\label{pf:waveform}
				See \cite{Clerckx2016a,Clerckx2018b}.
			\end{proof}

			\begin{proposition}\label{pr:ao}
				Every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_I^{\star},\boldsymbol{w}_P^{\star},\rho^{\star})$ of the proposed alternating algorithm is a stationary point of the original problem \ref{op:original}.
			\end{proposition}

			\begin{proof}\label{pf:ao}
				The objective function \ref{ob:original} is non-decreasing over iterations of Algorithm \ref{al:alternating}, which is also upper-bounded due to the unit-modulus constraint \ref{co:original_modulus} and the average transmit power constraint \ref{co:original_power}. Thus, Algorithm \ref{al:alternating} is guaranteed to converge, namely the sequence $\{\boldsymbol{\phi}^{(i)},\boldsymbol{w}_I^{(i)},\boldsymbol{w}_P^{(i)},\rho^{(i)}\}$ generated by optimizing $\boldsymbol{\phi}$ and $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$ alternatively has limit points. As demonstrated in \cite{Grippo2000,Hong2016,Li2013a}, the solution is a stationary point of problem \ref{op:original}.
			\end{proof}
		\end{subsubsection}
	\end{subsection}
\end{section}
